Barriers to meaningful data sharing

### 2021-04-01 new-paper.Rmd
change minimally acceptable practices to minimal set of practices

Tools to prepare datasets and metadata (*the infrastructure*) and minimally acceptable practices (*guidelines*) for reuse are sparse [@Arslan2019; @Roche2015]. Unlike code, datasets are far more diverse in terms of heterogeneity, size, and formats. This makes them particularly challenging to standardize or easily "install" where the code is running. There are some efforts working towards improving this process, such as gogetdata , the 'dat' project, and a private company, Quilt [@goget; @dat; @quilt].

@@

To make data more reusable, we need to make it easier to generate metadata, standardise good practices within and across communities, and make reusable data sharing a recognized, normalised, part of research. Here we present a set of minimally acceptable practices to facilitate this change. These include documentation (Section \@ref(readme)), licensing (Section \@ref(licenses)), citation (Section \@ref(cite)), raw and analysis ready data (Section \@ref(rawdata)), code (Section \@ref(scripts)), and sharing in packages (Section \@ref(pkgs)). We also discuss considerations for sharing of data of various sizes (Section \@ref(size)).

>>>>

Tools to prepare datasets and metadata (*the infrastructure*) and minimal set of practices (*guidelines*) for reuse are sparse [@Arslan2019; @Roche2015]. Unlike code, datasets are far more diverse in terms of heterogeneity, size, and formats. This makes them particularly challenging to standardize or easily "install" where the code is running. There are some efforts working towards improving this process, such as gogetdata , the 'dat' project, and a private company, Quilt [@goget; @dat; @quilt].

@@

To make data more reusable, we need to make it easier to generate metadata, standardise good practices within and across communities, and make reusable data sharing a recognized, normalised, part of research. Here we present a set of minimal set of practices to facilitate this change. These include documentation (Section \@ref(readme)), licensing (Section \@ref(licenses)), citation (Section \@ref(cite)), raw and analysis ready data (Section \@ref(rawdata)), code (Section \@ref(scripts)), and sharing in packages (Section \@ref(pkgs)). We also discuss considerations for sharing of data of various sizes (Section \@ref(size)).
